### 2024-12-17 bericht/AGI_report_kraftjul.tex
initial

\documentclass{article}
\usepackage[margin=2.5cm]{geometry} % Set margins
\usepackage{graphicx}
\usepackage[absolute]{textpos} % Enable absolute positioning
\usepackage{titlesec} % Package for controlling section title appearance
\usepackage[scaled]{helvet}
\usepackage[T1]{fontenc}
\usepackage{fancyhdr}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{amsmath}

\usepackage{url} % Load the url package

% Set up hyperref
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    linkbordercolor={0 0 1},
    linktoc=none
}

% Set up references
\usepackage[
    backend=biber,             % Use biber backend (an external tool)
    sorting=none,              % Enumerates the reference in order of their appearance
    style=authoryear           % Choose here your preferred citation style
]{biblatex}
\addbibresource{bibliography.bib} % The filename of the bibliography
\usepackage[autostyle=true]{csquotes} 
                               % Required to generate language-dependent quotes 
                               % in the bibliography

\usepackage[german]{babel}     % Set the document language to German

\setlength{\TPHorizModule}{1cm} % Set horizontal unit of measure
\setlength{\TPVertModule}{1cm} % Set vertical unit of measure
\setlength{\parindent}{0pt}

\renewcommand{\familydefault}{\sfdefault}

\makeatletter
\renewcommand{\maketitle}{
  \begin{flushleft} 
    \Large\textmd{\@title} 
    \par
  \end{flushleft}
}
\makeatother

% Define style of sectiontitles
\titleformat{\section}
  {\normalfont\Large\mdseries}{\thesection}{1em}{}

\titleformat{\subsection}
  {\normalfont\large\mdseries} % Adjust style: smaller size, medium series (not italic)
  {} % No label
  {0pt} % Spacing between label and title
  {} % Code to execute after the title
\titlespacing*{\subsection}
  {0pt} % Left margin
  {0.8em} % Space above
  {0.4em} % Space below

% Set up fancyhdr
\fancyhf{} % Clear all headers and footers
\renewcommand{\headrulewidth}{0pt} % Remove the header rule
\rfoot{\thepage} % Place the page number in the right footer
\pagestyle{fancy}

% Add listings package for code highlighting
\usepackage{listings}
\usepackage{xcolor}
\usepackage{tcolorbox}

%%%%% Title %%%%%
\title{Individuelle Applikation zur georeferenzierten Datenerfassung}

\begin{document}

%%%%% Header %%%%%
\begin{textblock}{1}(2.5,1) % Position 1cm from left and 1cm from top
        \includegraphics[width=6cm]{logo.jpg} % Add logo
\end{textblock}

\begin{textblock}{6}(13,1) % Position 14cm from left and 1cm from top
        \raggedleft
        Annalisa Berger,
        Jonas Iseli, \\
        Pascal Kipf,
        Julian Kraft\\
        Digitale Agrodiagnostik\\
        \today
\end{textblock}

\vspace*{1.5cm}

%%%%% Document %%%%%

\maketitle

\tableofcontents

\section{Idee} %%%%%

Das Erfassen von georeferenzierten Daten ist eine häufige Aufgabe bei Forschung im Bereich 
Umweltnaturwissenschaften. Leider werden dabei noch oft Papier und Stift verwendet, was
die spätere Auswertung und Verarbeitung der Daten erschwert. Die Idee ist es, einen Bausatz für Applikationen
zu entwickeln, der es ermöglicht, massgeschneiderte Applikationen für die georeferenzierte Datenerfassung
zu erstellen. Die Applikation soll es ermöglichen, georeferenzierte Daten direkt auf dem Feld mit dem Smartphone
zu erfassen. Die Georeferenzierung soll dabei automatisch mit Hilfe des GPS-Moduls des Smartphones
erfolgen. Die Daten sollen in einer eigenen Datenbank gespeichert werden, um die Datensicherheit zu gewährleisten.

\section{Vorprojekt} %%%%%

\subsection{Marktanalyse} %----

Eine Marktanalyse hat ergeben, dass es bereits einige Applikationen gibt, die ähnliche Funktionen
anbieten. Beispiele dafür sind: \href{https://www.fastfieldforms.com/}{Fastfield},
\href{https://merginmaps.com/}{Mergin Maps}, \href{https://www.fulcrumapp.com/}{Fulcrum} und 
diverse mehr. Diese Applikationen sind jedoch meistens sehr teuer und bieten viele Funktionen, die
für den Anwendungszweck nicht benötigt werden. Dazu kommt im Zusammenhang mit Forschung die
Problematik der Datensicherheit. In fast allen Fällen werden die Daten auf dem Server des Anbieters
gespeichert, was für Forschungszwecke nicht immer ideal ist.

\subsection{Nutzen für die Anwender} %----

Das Erfassen von georeferenzierten Daten muss nicht mehr mühsam mit Papier und Stift erfolgen - somit
fällt das spätere Übertragen der Daten in eine digitale Form weg. Dadurch wird die Fehleranfälligkeit
der Datenerfassung reduziert. Die Daten sind sicher in einer eigenen Datenbank gespeichert und die
Kontrolle über die Daten bleibt beim Anwender.

\subsection{Marketingstrategie} %----

Die Idee ist es, den Bausatz für die Applikation open-source zu veröffentlichen. Jeder, der in der Lage ist,
damit selbst eine Applikation zu erstellen, kann dies tun. Für Anwender, die nicht in der Lage sind,
damit eine für sie massgeschneiderte Applikation zu erstellen, wird ein Service angeboten, bei dem
die Applikation für sie erstellt wird. Dieser Service wird kostenpflichtig sein und wird nach Aufwand
verrechnet. Wann immer möglich, soll der Service aber mit den IT Ressourcen der Anwender beziehungsweise
der Forschungseinrichtung durchgeführt werden. Da das ganze nicht kommerziell ist, wird keine Werbung
geschaltet. Lediglich sollen potentielle Anwender über die Existenz des Bausatzes und die Möglichkeit
für Unterstützung informiert werden.

\subsection{Technische Machbarkeit} %----

Die technische Machbarkeit wurde bereits mittels eines Prototyps überprüft, der eine einfache Applikation
zur Erfassung von Wildtiersichtungen ermöglicht. Die Technische Machbarkeit auf der Seite der
Lokalen Anwendung auf dem Smartphone wurde bestätigt. Die Machbarkeit, das ganze in die IT Infrastruktur
einer Forschungseinrichtung zu integrieren, muss von Fall zu Fall mit den entsprechenden IT-Verantwortlichen
geklärt werden.

\section{Projekt} %%%%%

\subsection{Name und Branding} %----

Da es sich nicht um ein kommerzielles Projekt handelt, wird auf ein Branding verzichtet. Die Funktionalität
und die Einfachheit der Applikation sollen im Vordergrund stehen. Es soll keinerlei Ablenkungen vom
wesentlichen Zweck der Applikation geben. Ein Name für die Applikation kann natürlich bei jeder Anwendung individuell gewählt werden. 
Für diesen Prototyp wurde der äusserst kreative Name "Wildtierapp" gewählt.\\

Etwas mehr Kreativität hat die Designabteilung unter der Leitung von Annalisa Berger bei der Gestaltung des Logos
an den Tag gelegt. Das fertige Logo für die Applikation sieht wie folgt aus: \\

\begin{center}
  \includegraphics[width=0.3\textwidth]{"logo_app.png"}
\end{center}

Verschiedene Elemente des wesentlichen Zwecks der Applikation sind im Logo enthalten. Es wird ein Geo-Tag und die Erde als Karten Grid dargestellt
um den Zweck der georeferenzierten Datenerfassung zu symbolisieren. Der Hirsch und der Adler sind Symbole für die Wildtiere,
die den Inhalt der Daten repräsentieren. Die Idee ist es, dass für jede Anwendung eine Ableitung
dieses Logos verwendet werden kann, indem der Hirsch und der Adler durch Symbole ausgetauscht werden, die
für die spezifische Anwendung relevant sind.

\newpage

\subsection{Prototyp} %----

Der Prototyp ist eine einfache Applikation zur Erfassung von Wildtiersichtungen. Die Applikation
wird auf einem privaten Server gehostet und die Daten werden in einer Datenbank auf demselben Server gespeichert.\\

Die Applikation kann unter folgendem Link aufgerufen werden - allerdings funktioniert es nur mit dem Google Chrome Browser:\\

\begin{center}

  \includegraphics[width=3cm]{qr_code_app.png}\\
  \url{https://wildtierapp.juliankraft.ch/app/}

\end{center}

Die erhobenen Daten können unter folgendem Link eingesehen werden:\\

\begin{center}

  \includegraphics[width=3cm]{qr_code_data.png}\\
  \url{https://wildtierapp.juliankraft.ch/}

\end{center}

Für den effektiven Datenzugriff um diese weiter verarbeiten zu können gibt es einen API Endpunkt um auf die SQL Datenbank zuzugreifen.

\newpage

\subsection{SWOT-Analyse} %----

\begin{minipage}{0.5\textwidth}
  \begin{tcolorbox}[title=Strengths (Stärken), colframe=blue!50!black, colback=blue!10, height=6cm]
    \begin{itemize}
        \item Sehr individuell
        \item einfach und beschränkt auf das Wesentliche
        \item Absolute Kontrolle über die Daten
        \item Open-Source
    \end{itemize}
  \end{tcolorbox}
\end{minipage}
\hfill
\begin{minipage}{0.5\textwidth}
  \begin{tcolorbox}[title=Weaknesses (Schwächen), colframe=red!50!black, colback=red!10, height=6cm]
    \begin{itemize}
        \item Browser basiert
        \item Programmierkenntnisse notwendig
        \item limitierte Funktionalität
        \item Läuft aktuell noch mit dem Kartenservice von Google (Google Maps)
    \end{itemize}
  \end{tcolorbox}
\end{minipage}

\vspace{1cm}

\begin{minipage}{0.5\textwidth}
  \begin{tcolorbox}[title=Opportunities (Chancen), colframe=green!50!black, colback=green!10, height=6cm]
    \begin{itemize}
        \item Open-Source - andere könnten Funktionalität erweitern und verbessern
        \item Unabhängigkeit von kommerziellen Anbietern
        \item Möglichkeit für Forschungseinrichtungen, eigene Applikationen zu erstellen
    \end{itemize}
  \end{tcolorbox}
\end{minipage}
\hfill
\begin{minipage}{0.5\textwidth}
  \begin{tcolorbox}[title=Threats (Gefahren), colframe=orange!50!black, colback=orange!10, height=6cm]
    \begin{itemize}
        \item Niemand interessiert sich dafür
        \item es könnte abschreckend wirken, dass Programmierkenntnisse notwendig sind
        \item Konkurrenz durch kommerzielle Anbieter
    \end{itemize}
  \end{tcolorbox}
\end{minipage}

\newpage

\section{Umsetzung} %%%%%

\subsection{Zeitplan} %----

Da schon ein Prototyp existiert, kann die Umsetzung relativ schnell erfolgen. Als nächster Schritt wird
ein konkretes Projekt benötigt, wo tatsächlich georeferenzierte Daten erfasst werden müssen. Die Applikation
wird dann entsprechend angepasst und erweitert. Die Umsetzung wird in enger Zusammenarbeit mit den
Anwendern erfolgen, um sicherzustellen, dass die Applikation den Anforderungen entspricht.
Falls ein Projekt gefunden wird, und das Hosting auf einem Server der Forschungseinrichtung möglich ist,
oder einer anderen geeigneten Lösung gefunden wurde, kann die Umsetzung in einem Monaten abgeschlossen sein.

\subsection{Budget} %----

Für die Umsetzung eines konkreten Projekts wird der Lohn für einen Programmierer für ca. einen Monat benötigt.
Dazu kommen noch allfällige Kosten für das Hosting der Applikation. Die Kosten dafür sind gering und
abhängig von der Laufzeit des Projekts - Server, die das handeln können sind schon für rund 50.-/Monat zu haben.
Je nach Grösse des Projekts können auch noch Kosten für den
Kartenservice von Google anfallen - dies kann aber auch umgegangen werden, indem ein anderer Kartenservice
wie zum Beispiel OpenStreetMap verwendet wird.

\subsection{Ausblick} %----

Da die Applikation open-source ist, besteht die Möglichkeit, dass andere Forschungseinrichtungen
sie ebenfalls nutzen. Dabei ist zu hoffen, dass die Funktionalität der Applikation durch die
Beiträge anderer verbessert wird. Es könnten auch neue Funktionalitäten hinzugefügt werden wie zum
Beispiel die Möglichkeit, Bilder zu den Daten hinzuzufügen.

\section*{Deklaration zu AI Tool Nutzung} %%%%%

Zum Erstellen dieses Dokumentes wurde ChatGPT und GitHub copilot verwendet.
Auch bei der Programmierung des Prototyps kam vie AI zum Einsatz.

\end{document}

### 2024-12-17 presentation/present.sh
changed path for present.sh

@@ -1,0 +1,1 @@
+reveal-md presentation.md --static ~/go/wildtier_erhebung_backend/static/presentation/

### 2024-12-17 presentation/present.sh
update presentation styles and add custom logo support

@@ -1,1 +1,3 @@
-reveal-md presentation.md --static ~/go/wildtier_erhebung_backend/static/presentation/
+reveal-md presentation.md --css simple_jk.css --static ~/go/wildtier_erhebung_backend/static/presentation/
+# i want to copy the logo to the static folder
+cp ./images/logo.jpg ~/go/wildtier_erhebung_backend/static/presentation/images/logo.jpg

### 2024-12-17 presentation/present.sh
refactor present.sh script for improved structure and error handling; update presentation.md links to open in new tab

@@ -1,3 +1,37 @@
-reveal-md presentation.md --css simple_jk.css --static ~/go/wildtier_erhebung_backend/static/presentation/
-# i want to copy the logo to the static folder
-cp ./images/logo.jpg ~/go/wildtier_erhebung_backend/static/presentation/images/logo.jpg
+#!/bin/bash
+
+# Variables
+TARGET_FOLDER=~/go/wildtier_erhebung_backend/static/presentation/
+SOURCE_IMAGES=./images
+LOGO_IMAGE=logo.jpg
+
+# Clear the target folder if it exists
+if [ -d "$TARGET_FOLDER" ]; then
+    rm -rf "$TARGET_FOLDER"
+    echo "Cleared target folder: $TARGET_FOLDER"
+else
+    echo "Target folder does not exist. No need to clear."
+fi
+
+# Export the presentation
+reveal-md presentation.md --css simple_jk.css --static "$TARGET_FOLDER"
+if [ $? -eq 0 ]; then
+    echo "Presentation exported successfully to $TARGET_FOLDER!"
+else
+    echo "Error: Failed to export presentation." >&2
+    exit 1
+fi
+
+# Create images folder if it doesn't exist
+mkdir -p "$TARGET_FOLDER/images"
+
+# Copy logo to the static folder
+if [ -f "$SOURCE_IMAGES/$LOGO_IMAGE" ]; then
+    cp "$SOURCE_IMAGES/$LOGO_IMAGE" "$TARGET_FOLDER/images/"
+    echo "Logo ($LOGO_IMAGE) copied to $TARGET_FOLDER/images/"
+else
+    echo "Error: Logo file ($SOURCE_IMAGES/$LOGO_IMAGE) not found." >&2
+    exit 1
+fi
+
+echo "Script completed successfully!"

### 2024-12-17 bericht/AGI_report_kraftjul.tex
add .gitignore to exclude build artifacts and temporary files; add initial bibliography entries for Go, Ionic, and MariaDB

@@
     sorting=none,              % Enumerates the reference in order of their appearance
-    style=authoryear           % Choose here your preferred citation style
+    style=numeric           % Choose here your preferred citation style
 ]{biblatex}
-\addbibresource{bibliography.bib} % The filename of the bibliography
+\addbibresource{agi_projekt.bib} % The filename of the bibliography
+
 \usepackage[autostyle=true]{csquotes} 
@@
                                % in the bibliography
+
+% Customize citation number color
+\usepackage{xcolor} % Ensure xcolor is loaded
+\DeclareFieldFormat{biblabel}{\textcolor{blue}{[#1]}} % Set citation color to blue
+\renewcommand*{\mkbibbrackets}[1]{\textcolor{black}{[#1]}} % Ensure brackets are also black
 
@@
 %%%%% Title %%%%%
-\title{Individuelle Applikation zur georeferenzierten Datenerfassung}
+\title{WebApp zur Erfassung von Wildtiersichtungen}
 
@@
 \begin{textblock}{1}(2.5,1) % Position 1cm from left and 1cm from top
-        \includegraphics[width=6cm]{logo.jpg} % Add logo
+        \includegraphics[width=6cm]{images/logo.jpg} % Add logo
 \end{textblock}
@@
         \raggedleft
-        Annalisa Berger,
-        Jonas Iseli, \\
-        Pascal Kipf,
-        Julian Kraft\\
-        Digitale Agrodiagnostik\\
+        Julian Kraft UI22\\
+        Angewandte Geoinformatik\\
         \today
@@
 
-\section{Idee} %%%%%
+\section{Einleitung} %%%%%
 
-Das Erfassen von georeferenzierten Daten ist eine häufige Aufgabe bei Forschung im Bereich 
-Umweltnaturwissenschaften. Leider werden dabei noch oft Papier und Stift verwendet, was
-die spätere Auswertung und Verarbeitung der Daten erschwert. Die Idee ist es, einen Bausatz für Applikationen
-zu entwickeln, der es ermöglicht, massgeschneiderte Applikationen für die georeferenzierte Datenerfassung
-zu erstellen. Die Applikation soll es ermöglichen, georeferenzierte Daten direkt auf dem Feld mit dem Smartphone
-zu erfassen. Die Georeferenzierung soll dabei automatisch mit Hilfe des GPS-Moduls des Smartphones
-erfolgen. Die Daten sollen in einer eigenen Datenbank gespeichert werden, um die Datensicherheit zu gewährleisten.
+Im Zentrum jedes Projekts mit Geodaten stehen die Daten. Wenn man diese noch nicht hat, geht es darum eine
+geeignete Methode zu finden, um diese zu erfassen. Im Bereich Umweltnaturwissenschaften sind das noch
+immer oft manuell erhobene Daten. Auch diese Feldarbeit kann jedoch durch den Einsatz von Technologie
+vereinfacht werden. Ein geeignetes Tool dafür besitzt so ziemlich jeder - das Smartphone.
+Eine kurze Online-Recherche zeigt, dass es bereits viele Apps gibt, die das können. Jedoch sind diese
+oft relativ teuer, können viel mehr als das was man braucht und die Datenhoheit ist oft beim Anbieter der App.
+Bei all den Modernen Frameworks und Programmiersprachen kann das doch nicht so schwer sein, eine eigene App
+zu schreiben, die genau das macht, was man will. Und so entstand die Idee, eine eigene App zu erstellen.
+In dieser Arbeit soll geprüft werden, wie schwer es wirklich ist, eine eigene App zu erstellen und das
+mit sehr begrenzten Vorkenntnissen, viel Trial and Error, unglaublich viel Recherchen, dem
+Einsatz von AI, viel Geduld und etwas bis etwas mehr Unterstützung von einem erfahrenen Entwickler.
+Genau mit dieser Unterstützung wurde dann auch begonnen. Um nicht alles von Grund auf herausfinden zu müssen,
+wurde mit einem Beratungsgespräch begonnen. Dabei wurde die Idee vorgestellt. Es wurde besprochen, welche
+Technologien, Programmiersprachen und Frameworks zielführend, machbar und sinnvoll sind.
+In einem weiteren Termin wurde dann gemeinsam der Server konfiguriert und die Entwicklungsumgebung eingerichtet.
+Ein nicht so kleiner Crashkurs hat dann einen guten Einstieg ins Projekt erleichtert.
 
-\section{Vorprojekt} %%%%%
+\section{Methoden} %%%%%
 
-\subsection{Marktanalyse} %----
+Die App besteht im Wesentlichen aus drei Teilen: Dem webbasierten Frontend, dem Backend Server und der Datenbank.
+Diese drei Teile sind miteinander verbunden und kommunizieren miteinander. Das Frontend ist die Benutzeroberfläche,
+die man auf dem Smartphone zu sehen bekommt. Das Backend ist die Logik, die im Hintergrund abläuft und die Datenbank
+ist der Speicherort für alle Daten, die abgerufen oder gespeichert werden.
 
-Eine Marktanalyse hat ergeben, dass es bereits einige Applikationen gibt, die ähnliche Funktionen
-anbieten. Beispiele dafür sind: \href{https://www.fastfieldforms.com/}{Fastfield},
-\href{https://merginmaps.com/}{Mergin Maps}, \href{https://www.fulcrumapp.com/}{Fulcrum} und 
-diverse mehr. Diese Applikationen sind jedoch meistens sehr teuer und bieten viele Funktionen, die
-für den Anwendungszweck nicht benötigt werden. Dazu kommt im Zusammenhang mit Forschung die
-Problematik der Datensicherheit. In fast allen Fällen werden die Daten auf dem Server des Anbieters
-gespeichert, was für Forschungszwecke nicht immer ideal ist.
+\subsection{Frontend} %%%%%
 
-\subsection{Nutzen für die Anwender} %----
+Das Frontend wurde mit dem Framework Ionic erstellt. Ionic ist ein open source toolkit für die Entwicklung von
+mobile User Interfaces. Es basiert auf Angular, einem weiteren open source Framework, das von Google entwickelt wurde.
+Es ermöglicht die Erstellung von Webanwendungen, die auf allen Plattformen - Android, iOS und Web - laufen und dabei
+eine native App-ähnliche Performance und Erfahrung bieten. \autocite{IonicFrameworkCrossPlatform}
+Das Framework ermöglicht es relativ einfach ein Projekt zu starten und in einer Entwicklungsumgebung zu testen.
+Dabei wird die App im Browser angezeigt. Das effektive programmieren geschieht dann in den Programmiersprachen
+HTML, CSS und TypeScript. TypeScript ist eine von Microsoft entwickelte Programmiersprache, die auf JavaScript basiert.
+CSS ist eine Stylesheet-Sprache, die für das Design der Benutzeroberfläche verwendet wird. HTML ist eine Markup-Sprache,
+die für die Struktur der Benutzeroberfläche verwendet wird.
 
-Das Erfassen von georeferenzierten Daten muss nicht mehr mühsam mit Papier und Stift erfolgen - somit
-fällt das spätere Übertragen der Daten in eine digitale Form weg. Dadurch wird die Fehleranfälligkeit
-der Datenerfassung reduziert. Die Daten sind sicher in einer eigenen Datenbank gespeichert und die
-Kontrolle über die Daten bleibt beim Anwender.
+\subsection{Backend} %%%%%
 
-\subsection{Marketingstrategie} %----
+Das Backend wurde mit der Programmiersprache Go erstellt. Go ist eine von Google entwickelte Programmiersprache,
+die für die Entwicklung von Webanwendungen und Servern verwendet wird. Sie ist einfach zu lernen und zu verwenden
+und bietet eine gute Performance \autocite{GoProgrammingLanguage}. Auch soll erwähnt sein, dass GitHub Copilot
+für die Programmiersprache Go ausgezeichnete Vorschläge macht und so das Programmieren massiv erleichtert.
+Die Wesentlichen Logiken, die vom Backend in der App ablaufen sind die Authentifizierung des Benutzers, den Zugriff
+auf die Datenbank um beispielsweise verfügbare User zu prüfen oder die Auswahlmöglichkeiten bei den Tieren abzurufen
+und das Transformieren und Speichern von neuen Daten in der Datenbank.
 
-Die Idee ist es, den Bausatz für die Applikation open-source zu veröffentlichen. Jeder, der in der Lage ist,
-damit selbst eine Applikation zu erstellen, kann dies tun. Für Anwender, die nicht in der Lage sind,
-damit eine für sie massgeschneiderte Applikation zu erstellen, wird ein Service angeboten, bei dem
-die Applikation für sie erstellt wird. Dieser Service wird kostenpflichtig sein und wird nach Aufwand
-verrechnet. Wann immer möglich, soll der Service aber mit den IT Ressourcen der Anwender beziehungsweise
-der Forschungseinrichtung durchgeführt werden. Da das ganze nicht kommerziell ist, wird keine Werbung
-geschaltet. Lediglich sollen potentielle Anwender über die Existenz des Bausatzes und die Möglichkeit
-für Unterstützung informiert werden.
+\subsection{Datenbank} %%%%%
 
-\subsection{Technische Machbarkeit} %----
+Die verwendete Datenbank ist MariaDB. MariaDB ist eine von MySQL abgeleitete relationale Datenbank, die von der
+Open-Source-Community entwickelt wird. Sie ist einfach zu installieren und zu verwenden und bietet eine gute Performance \autocite{MariaDBFoundation}.
+In diesem Fall wurde Docker verwendet, um die Datenbank auf dem Server zu installieren und in einem 
+sogenannten Container zu betreiben. Die Datenbank besteht aus drei Tabellen: User, Animals und Sightings.
 
-Die technische Machbarkeit wurde bereits mittels eines Prototyps überprüft, der eine einfache Applikation
-zur Erfassung von Wildtiersichtungen ermöglicht. Die Technische Machbarkeit auf der Seite der
-Lokalen Anwendung auf dem Smartphone wurde bestätigt. Die Machbarkeit, das ganze in die IT Infrastruktur
-einer Forschungseinrichtung zu integrieren, muss von Fall zu Fall mit den entsprechenden IT-Verantwortlichen
-geklärt werden.
+\section{Resultate} %%%%%
 
-\section{Projekt} %%%%%
+\section{Diskussion} %%%%%
 
-\subsection{Name und Branding} %----
+\section{Acknowledgements und Deklaration} %%%%%
 
-Da es sich nicht um ein kommerzielles Projekt handelt, wird auf ein Branding verzichtet. Die Funktionalität
-und die Einfachheit der Applikation sollen im Vordergrund stehen. Es soll keinerlei Ablenkungen vom
-wesentlichen Zweck der Applikation geben. Ein Name für die Applikation kann natürlich bei jeder Anwendung individuell gewählt werden. 
-Für diesen Prototyp wurde der äusserst kreative Name "Wildtierapp" gewählt.\\
+Danke an Ramon Ott für die Unterstützung bei der Umsetzung dieses Projektes.
 
-Etwas mehr Kreativität hat die Designabteilung unter der Leitung von Annalisa Berger bei der Gestaltung des Logos
-an den Tag gelegt. Das fertige Logo für die Applikation sieht wie folgt aus: \\
-
-\begin{center}
-  \includegraphics[width=0.3\textwidth]{"logo_app.png"}
-\end{center}
-
-Verschiedene Elemente des wesentlichen Zwecks der Applikation sind im Logo enthalten. Es wird ein Geo-Tag und die Erde als Karten Grid dargestellt
-um den Zweck der georeferenzierten Datenerfassung zu symbolisieren. Der Hirsch und der Adler sind Symbole für die Wildtiere,
-die den Inhalt der Daten repräsentieren. Die Idee ist es, dass für jede Anwendung eine Ableitung
-dieses Logos verwendet werden kann, indem der Hirsch und der Adler durch Symbole ausgetauscht werden, die
-für die spezifische Anwendung relevant sind.
-
-\newpage
-
-\subsection{Prototyp} %----
-
-Der Prototyp ist eine einfache Applikation zur Erfassung von Wildtiersichtungen. Die Applikation
-wird auf einem privaten Server gehostet und die Daten werden in einer Datenbank auf demselben Server gespeichert.\\
-
-Die Applikation kann unter folgendem Link aufgerufen werden - allerdings funktioniert es nur mit dem Google Chrome Browser:\\
-
-\begin{center}
-
-  \includegraphics[width=3cm]{qr_code_app.png}\\
-  \url{https://wildtierapp.juliankraft.ch/app/}
-
-\end{center}
-
-Die erhobenen Daten können unter folgendem Link eingesehen werden:\\
-
-\begin{center}
-
-  \includegraphics[width=3cm]{qr_code_data.png}\\
-  \url{https://wildtierapp.juliankraft.ch/}
-
-\end{center}
-
-Für den effektiven Datenzugriff um diese weiter verarbeiten zu können gibt es einen API Endpunkt um auf die SQL Datenbank zuzugreifen.
-
-\newpage
-
-\subsection{SWOT-Analyse} %----
-
-\begin{minipage}{0.5\textwidth}
-  \begin{tcolorbox}[title=Strengths (Stärken), colframe=blue!50!black, colback=blue!10, height=6cm]
-    \begin{itemize}
-        \item Sehr individuell
-        \item einfach und beschränkt auf das Wesentliche
-        \item Absolute Kontrolle über die Daten
-        \item Open-Source
-    \end{itemize}
-  \end{tcolorbox}
-\end{minipage}
-\hfill
-\begin{minipage}{0.5\textwidth}
-  \begin{tcolorbox}[title=Weaknesses (Schwächen), colframe=red!50!black, colback=red!10, height=6cm]
-    \begin{itemize}
-        \item Browser basiert
-        \item Programmierkenntnisse notwendig
-        \item limitierte Funktionalität
-        \item Läuft aktuell noch mit dem Kartenservice von Google (Google Maps)
-    \end{itemize}
-  \end{tcolorbox}
-\end{minipage}
-
-\vspace{1cm}
-
-\begin{minipage}{0.5\textwidth}
-  \begin{tcolorbox}[title=Opportunities (Chancen), colframe=green!50!black, colback=green!10, height=6cm]
-    \begin{itemize}
-        \item Open-Source - andere könnten Funktionalität erweitern und verbessern
-        \item Unabhängigkeit von kommerziellen Anbietern
-        \item Möglichkeit für Forschungseinrichtungen, eigene Applikationen zu erstellen
-    \end{itemize}
-  \end{tcolorbox}
-\end{minipage}
-\hfill
-\begin{minipage}{0.5\textwidth}
-  \begin{tcolorbox}[title=Threats (Gefahren), colframe=orange!50!black, colback=orange!10, height=6cm]
-    \begin{itemize}
-        \item Niemand interessiert sich dafür
-        \item es könnte abschreckend wirken, dass Programmierkenntnisse notwendig sind
-        \item Konkurrenz durch kommerzielle Anbieter
-    \end{itemize}
-  \end{tcolorbox}
-\end{minipage}
-
-\newpage
-
-\section{Umsetzung} %%%%%
-
-\subsection{Zeitplan} %----
-
-Da schon ein Prototyp existiert, kann die Umsetzung relativ schnell erfolgen. Als nächster Schritt wird
-ein konkretes Projekt benötigt, wo tatsächlich georeferenzierte Daten erfasst werden müssen. Die Applikation
-wird dann entsprechend angepasst und erweitert. Die Umsetzung wird in enger Zusammenarbeit mit den
-Anwendern erfolgen, um sicherzustellen, dass die Applikation den Anforderungen entspricht.
-Falls ein Projekt gefunden wird, und das Hosting auf einem Server der Forschungseinrichtung möglich ist,
-oder einer anderen geeigneten Lösung gefunden wurde, kann die Umsetzung in einem Monaten abgeschlossen sein.
-
-\subsection{Budget} %----
-
-Für die Umsetzung eines konkreten Projekts wird der Lohn für einen Programmierer für ca. einen Monat benötigt.
-Dazu kommen noch allfällige Kosten für das Hosting der Applikation. Die Kosten dafür sind gering und
-abhängig von der Laufzeit des Projekts - Server, die das handeln können sind schon für rund 50.-/Monat zu haben.
-Je nach Grösse des Projekts können auch noch Kosten für den
-Kartenservice von Google anfallen - dies kann aber auch umgegangen werden, indem ein anderer Kartenservice
-wie zum Beispiel OpenStreetMap verwendet wird.
-
-\subsection{Ausblick} %----
-
-Da die Applikation open-source ist, besteht die Möglichkeit, dass andere Forschungseinrichtungen
-sie ebenfalls nutzen. Dabei ist zu hoffen, dass die Funktionalität der Applikation durch die
-Beiträge anderer verbessert wird. Es könnten auch neue Funktionalitäten hinzugefügt werden wie zum
-Beispiel die Möglichkeit, Bilder zu den Daten hinzuzufügen.
-
-\section*{Deklaration zu AI Tool Nutzung} %%%%%
+Danke an Annalisa Berger für das Design des Logos.
 

### 2024-12-17 bericht/AGI_report_kraftjul.tex
update AGI_report_kraftjul.tex to customize citation colors and add bibliography section

@@
 % Customize citation number color
-\usepackage{xcolor} % Ensure xcolor is loaded
-\DeclareFieldFormat{biblabel}{\textcolor{blue}{[#1]}} % Set citation color to blue
-\renewcommand*{\mkbibbrackets}[1]{\textcolor{black}{[#1]}} % Ensure brackets are also black
+\usepackage{xcolor} % Load xcolor for color customization
+
+% Change the color of citation numbers and brackets in text
+\renewcommand*{\mkbibbrackets}[1]{\textcolor{blue}{[#1]}} % Brackets and numbers in blue
+
+% Change the color of numbers in the bibliography
+\DeclareFieldFormat{labelnumber}{\textcolor{blue}{#1}}
 
@@
 
+\printbibliography
+
 \end{document}

### 2024-12-17 article/example.tex
remove obsolete bibliography entries for Go, Ionic, and MariaDB; add new comprehensive bibliography file for JOSIS articles and EPS graphics

%% josis.tex 1.4   2016-09-15    JoSIS latex template
%------------------------------------------------------------------
% Filename: josis_template.tex
%
% This file is intended as a template for typesetting articles for the
%
%                        Journal of Spatial Information Science.
%
% Please edit this template to generate your own formatted manuscripts
% for submission to JOSIS. See http://josis.org for further details.
%

%%% JOSIS checks in typesetting
%%% * All titles and sections lower case *EXCEPT short title  [ ]
%%% * Remove author postal addresses, only have geographic places and institutions [ ] 
%%% * Consistent use of Section, Figure, Table (capitalized and in full) [ ]
%%% * 10 keywords (and all lower case) [ ]
%%% * Remove all avoidable footnotes [ ]
%%% * Use double quotation marks (``'' not "" or `') [ ]
%%% * Punctuation inside quotations [ ]
%%% * E.g. and i.e. followed by comma [ ]
%%% * cf. followed by tilde [ ]
%%% * Itemize and enumerate correctly punctuated [e.g., "1. x, 2. y, and 3. x." ]
%%% * And/or lists using American English punctuation (e.g., "x, y, and z") [ ] 
%%% * Bibliography (e.g., en-dashes for number ranges, consistent "Proc.~" for Proceedings of..., etc.) []
%%% * Acknowledgment style use section* [ ] 
%%% * et al. no italics, but with dot  [ ] 
%%% * All captions end with full stop  [ ] 
%%% * Table captions under, not over table  [ ]
%%% * Adjust urls with burlalt [ ] 
%%% * Check correct use of hyphens, emdashes, endashes  [ ]
%%% * Perform spell check  [ ]

%%% JOSIS checks directly before publication 
%%% Check DOI, page numbers on article and web site. [ ]
%%% Update web site with final title, abstract, keywords. [ ] 
%%% Build with distiller for DOI links. [ ]

% Required documentclass definition for JOSIS
\documentclass{josis}
\usepackage{hyperref}
\usepackage[hyphenbreaks]{breakurl}
\usepackage{booktabs}
\usepackage{stmaryrd}
\usepackage[T1]{fontenc}
\usepackage{cite}

% Suggested packages for algorithm formatting
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algpseudocode}

\usepackage[table]{xcolor}
\usepackage{amssymb,amsmath}

\renewcommand{\topfraction}{0.9} 
\renewcommand{\textfraction}{0.1}

% Page setup and overhangs
\sloppy
\widowpenalty=10000
\clubpenalty=10000
\hyphenpenalty=75

% Article details for accepted manuscripts will be added by editorial staff
% Omit year if article in press
% Omit number if article under review
\josisdetails{%
   number=N, year=YYYY, firstpage=xx, lastpage=yy, 
  doi={10.5311/JOSIS.YYYY.II.NNN},
   received={December 18, 2024}, 
   returned={},
   revised={},
   accepted={}, }

\newcommand{\mydoi}[1]{\href{http://dx.doi.org/#1}{doi:\protect\detokenize{#1}}}

%\renewcommand{\UrlLeft}{http:\sslash}
%\DeclareUrlCommand\myurl{\def\UrlLeft{}\def\UrlRight{}%
%\urlstyle{tt}}

\urlstyle{rm}
\makeatletter
% Inspired by http://anti.teamidiot.de/nei/2009/09/latex_url_slash_spacingkerning/
% but slightly less kern and shorter underscore
\let\UrlSpecialsOld\UrlSpecials
\def\UrlSpecials{\UrlSpecialsOld\do\/{\Url@slash}\do\_{\Url@underscore}}%
\def\Url@slash{\@ifnextchar/{\kern-.11em\mathchar47\kern-.2em}%
    {\kern-.0em\mathchar47\kern-.08em\penalty\UrlBigBreakPenalty}}
\def\Url@underscore{\nfss@text{\leavevmode \kern.06em\vbox{\hrule\@width.3em}}}
\makeatother

\hypersetup{
colorlinks=true,
linkcolor=black,
citecolor=black,
urlcolor=black
}

% Add the running author and running title information
\runningauthor{\begin{minipage}{.9\textwidth}\centering Julian Kraft\end{minipage}}
\runningtitle{Wildlife sightings WebApp}

% Document begins
\begin{document}
%\setcounter{page}{33}

% Insert your own title
\title{A Web Application for Wildlife Sightings - how accessible is this technology using modern frameworks?}

% Insert your manuscipts authors, affiliations, and addresses
\author{Julian Kraft}\affil{LSFM, ZHAW, Switzerland}

\maketitle

% Add 5-10 keywords for every submission
\keywords{Web Application, Wildlife Sightings, Geodata, Open Source, Web Frameworks}

% Add a short abstract of 150-250 words
\begin{abstract}
The aim of this semester project is to assess the accessability of the technology to create a web application to record geo tagged data.
With the help of modern web frameworks, a web application was built to record wildlife sightings. A working prototype was created and and made
available online with the option to install it on smartphones of all major operating systems.
The project was a success and the technology is accessible to everyone with a bit more than basic programming knowledge and maybe some help.

\end{abstract}

% Your main text begins here. 
\section{Introduction}

\section{Author guidelines}

\subsection{Manuscript preparation}
Manuscripts must be written in English in a clear, direct, and active style. All pages must be numbered sequentially. The manuscript should be submitted as a PDF file based on this \LaTeX template.

\subsection{Title}
The title should be concise, and must not be more than 20 words. Authors should also provide a short ``running title.''

\subsection{Authors and institutional affiliations}
Authors are required to provide their full names and their institutional affiliations, omitting postal addresses.

\subsection{Abstract}
The abstract should summarize the essential features of the article, and must not exceed 250 words for full papers. Abbreviations should be avoided in the abstract, and references should not be cited in the abstract.

\subsection{Keywords}
Your submission must include between five and ten keywords for your article. Accepted manuscripts must additionally specify further index terms as appropriate.

\subsection{Main Text}
The main text should be divided into separate sections, and may be further subdivided according to the areas to be discussed. The manuscript style must be uniform throughout the text using 11pt Palatino font. The first appearance of any abbreviations in the text should be preceded by the full term, unless it is a standard abbreviation or unit of measurement. Reference numbers should be given in square brackets in the text. Common or assimilated words from Latin or other languages should not be italicized, including per se, et al.

\subsection{Style}

Many examples of the journal style can be seen in existing JOSIS published articles, \url{http://josis.org}. Please pay particular attention to the following style requirements:

\begin{itemize}
\item Spelling: Please use standard American English spelling throughout.
\item Punctuation: JOSIS uses standard American English punctuation. In
particular, please ensure: 
\begin{itemize}
\item all lists items are always separated by
punctuation (e.g., ``a, b, and c'' but not ``a, b and c''); and 
\item commas and periods always appear inside quotation marks (e.g., ``x, y, and z.'' but not ``x, y, and z''.).
\end{itemize}
\item Capitalization: JOSIS style is to only use capitals only for the
beginning of sentences, proper nouns, names (e.g., Norman, ArcMap) and,
where appropriate, acronyms (e.g., GIS). Please avoid capitalization of
other words (e.g., ``geographic information systems (GIS)'' but not
``Geographic Information Systems (GIS)'') and in titles, including section headings (e.g., ``Affordance-based individuation of junctions in Open Street Map" but not ``Affordance-Based Individuation of Junctions in Open Street Map'').
\end{itemize}

\subsection{Figures}
Figures and Tables must be numbered consecutively with a concise explanatory caption, and must be referred to in the main text with capitalized reference (e.g., ``Figure \ref{fig:1}'' or ``Table \ref{tab:1}''). Figures and Tables must appear in the text close to where they are first referred to in the main text. Figure and table captions come below the figure or table. Do not collect figures or tables together at the end of the article. Authors of accepted articles will need to supply high quality versions of all figures as separate .eps (encapsulated postscript) files.

\begin{figure}[tbh]
\centering
\includegraphics[width=\textwidth]{Figure1}
\caption{An illustrative figure, after \cite{huck15.JOSIS}.}\label{fig:1}
\end{figure}

\begin{table}
\centering
\begin{tabular}{lrr}
\hline
Text column & Numerical column 1 & Numerical column 2\\
\hline
First row& 10 & 0.003\\
Second row& 52& 10.037\\
Third row& 729 & 150.315\\
...& ...& ...\\
\hline
\end{tabular}
\caption{Example table with preferred line rules and alignment.}\label{tab:1}
\end{table}

\subsection{Algorithms}

Algorithms should be formatted using standard algorithm packages where possible, as in Algorithm~\ref{alg:1}.

\begin{algorithm}[htb]
\caption{Example algorithm formatting after \cite{zhong16.IJGIS}} \label{alg:1}
\footnotesize
\begin{algorithmic} [1]                   % enter the algorithmic environment
\Require A finite set of two-dimensional points $P \subset \mathbb{R} \times \mathbb{R}$ and one parameter $\lambda \in \mathbb{R}$
\State Construct the Delaunay triangulation $DT(P)$ of $P$
\State $\Delta \gets DT(P)$
\State Construct the list $B$ of exterior edges of $DT(P)$
\State Sort the list $B$ in descending order of edge length
\State Initialize the $v\!-\!boundary$ function
\State Set the root ($r$) of $\mathbf{T}_{{\chi}}(P,\, \lambda)$ to be \{edge = $\emptyset$, oppositeVertex = $\emptyset$, length = $\emptyset$\} 
\State Construct the list of parent nodes ($PN$) for the elements in $B$
\State Set each element in $PN$ to be $r$
\State $O(P,\, \lambda) \gets \emptyset$
\While{$B$ is not empty} 
	\State $e = \{d_1,\, d_2\} \gets$ pop($B$)
	\State $p \gets$ pop($PN$)
	\State $o \gets$ opposite vertex of $e$ in $\Delta$
	\State $N \gets$ \{edge = $e$, oppositeVertex = $o$, length = $||e||$\}
	\State Insert $N$ in $\mathbf{T}_{{\chi}}(P,\, \lambda)$ as a child of $p$
	\State $node(d_1) \gets N$
	\State $node(d_2) \gets N$
	\State Append $N$ to $O(P,\, \lambda)$
	\If{$||e|| > \lambda$ \textbf{and} $v\!-\!boundary(o) = false$}
		\State Remove $e$ from $\Delta$
		\State $v\!-\!boundary(o) = true$
		\State Insert the arms of $e$ in $\Delta$ into $B$ in order of edge length
		\State Insert $N$ into $PN$ at the corresponding position of the arms of $e$ in $B$ 
	\EndIf
\EndWhile
\State \textbf{Return} $\chi(P,\, \lambda)$ formed by leaves of $\mathbf{T}_{{\chi}}(P,\, \lambda)$, $DT(P)$, $\mathbf{T}_{{\chi}}(P,\, \lambda)$ and $O(P,\, \lambda)$
\end{algorithmic}
\end{algorithm}

\subsection{Footnotes}
Footnotes are strongly discouraged in text. Where footnotes must be used, they should be numbered consecutively.

\section{References}
References must be listed in the numerical system (ACM). Citations must be numbered sequentially [in square brackets] in the main text. Full numbered references must be listed in the reference section in alphabetical order. The reference numbers must be finalized and the bibliography must be fully formatted before submission. Examples of citation styles included in the bibliography for this document include journal articles \cite{overEtAl2010,arkin}, authored books \cite{bailey}, edited books \cite{miller09.BOOK}, articles in proceedings \cite{champion11}, articles in books or collections \cite{Grosso12}, theses \cite{ruas99}, technical reports \cite{blasertr}, and web resources \cite{web}.

\subsection{DOIs}

All JOSIS articles must list the DOI of all references, where a DOI exists, see
\url{http://josis.org/index.php/josis/about/submissions#authorGuidelines} for examples. Please check carefully to add the DOIs for cited references,
adding DOIs to all references that have one. DOIs may be added in the ``doi'' field of the bibtex file.

DOIs can be found via \url{http://www.crossref.org/guestquery/} as well as many
other search engines and publisher pages (e.g., Scopus, SpringerLink).

\section{About JOSIS}

The Journal of Spatial Information Science (JOSIS) is an international, interdisciplinary, open-access journal dedicated to publishing high-quality, original research articles in spatial information science. The journal aims to publish research spanning the theoretical foundations of spatial and geographical information science, through computation with geospatial information, to technologies for geographical information use.

JOSIS encourages submissions from topics including, but not limited to spatial and spatiotemporal information systems; computational geometry, geocomputation, spatial algorithms; geovisualization, cartography, and geographical user interfaces; computing with spatiotemporal information under uncertainty; spatial cognition and qualitative spatial reasoning; spatial data models and structures; conceptual models of space and geoontology; distributed and parallel spatial computing, web-based GIS, and interoperability; context- and location-aware computing; and applications to GIS, spatial databases, location-based services, geosensor networks, and geosensor web. The journal publishes full-length original research articles, as well as survey-style review papers. In addition, the journal publishes shorter articles in three sections: reports from community activities, letters to the editors, and book reviews.

\section*{Acknowledgments}

Acknowledgments appear in a separate unnumbered section before the bibliography. Please acknowledge anyone (individual/company/institution) who has contributed to the study, including substantial contributions to the conception, design, acquisition of data; analysis and interpretation of data; drafting the manuscript; or provided critical comments resulting in revisions to content. For each author, please list the source(s) of any funding or financial contributions related to the study.

\bibliographystyle{josisacm}
\bibliography{josisexample}

\end{document}

### 2024-12-17 article/main.tex
remove obsolete bibliography entries for Go, Ionic, and MariaDB; add new comprehensive bibliography file for JOSIS articles and EPS graphics

--- 2024-12-17 article/example.tex
@@
 
-\subsection{Manuscript preparation}
-Manuscripts must be written in English in a clear, direct, and active style. All pages must be numbered sequentially. The manuscript should be submitted as a PDF file based on this \LaTeX template.
-
-\subsection{Title}
-The title should be concise, and must not be more than 20 words. Authors should also provide a short ``running title.''
-
-\subsection{Authors and institutional affiliations}
-Authors are required to provide their full names and their institutional affiliations, omitting postal addresses.
-
-\subsection{Abstract}
-The abstract should summarize the essential features of the article, and must not exceed 250 words for full papers.
-Abbreviations should be avoided in the abstract, and references should not be cited in the abstract.
-
-\subsection{Keywords}
-Your submission must include between five and ten keywords for your article. Accepted manuscripts must additionally specify further index terms as appropriate.
-
-\subsection{Main Text}
-The main text should be divided into separate sections, and may be further subdivided according to the areas to be discussed.
-The manuscript style must be uniform throughout the text using 11pt Palatino font.
-The first appearance of any abbreviations in the text should be preceded by the full term, unless it is a standard abbreviation or unit of measurement.
-Reference numbers should be given in square brackets in the text.
-Common or assimilated words from Latin or other languages should not be italicized, including per se, et al.
-
-\subsection{Style}
-
-Many examples of the journal style can be seen in existing JOSIS published articles, \url{http://josis.org}. Please pay particular attention to the following style requirements:
-
-\begin{itemize}
-\item Spelling: Please use standard American English spelling throughout.
-\item Punctuation: JOSIS uses standard American English punctuation. In
-particular, please ensure: 
-\begin{itemize}
-\item all lists items are always separated by
-punctuation (e.g., ``a, b, and c'' but not ``a, b and c''); and 
-\item commas and periods always appear inside quotation marks (e.g., ``x, y, and z.'' but not ``x, y, and z''.).
-\end{itemize}
-\item Capitalization: JOSIS style is to only use capitals only for the
-beginning of sentences, proper nouns, names (e.g., Norman, ArcMap) and,
-where appropriate, acronyms (e.g., GIS). Please avoid capitalization of
-other words (e.g., ``geographic information systems (GIS)'' but not
-``Geographic Information Systems (GIS)'') and in titles, including section headings (e.g., ``Affordance-based individuation of junctions in Open Street Map" but not ``Affordance-Based Individuation of Junctions in Open Street Map'').
-\end{itemize}
-
-\subsection{Figures}
-Figures and Tables must be numbered consecutively with a concise explanatory caption, and must be referred to in the main text with capitalized reference (e.g., ``Figure \ref{fig:1}'' or ``Table \ref{tab:1}'').
-Figures and Tables must appear in the text close to where they are first referred to in the main text.
-Figure and table captions come below the figure or table.
-Do not collect figures or tables together at the end of the article.
-Authors of accepted articles will need to supply high quality versions of all figures as separate .eps (encapsulated postscript) files.
-
-\begin{figure}[tbh]
-\centering
-\includegraphics[width=\textwidth]{Figure1}
-\caption{An illustrative figure, after \cite{huck15.JOSIS}.}\label{fig:1}
-\end{figure}
-
-\begin{table}
-\centering
-\begin{tabular}{lrr}
-\hline
-Text column & Numerical column 1 & Numerical column 2\\
-\hline
-First row& 10 & 0.003\\
-Second row& 52& 10.037\\
-Third row& 729 & 150.315\\
-...& ...& ...\\
-\hline
-\end{tabular}
-\caption{Example table with preferred line rules and alignment.}\label{tab:1}
-\end{table}
-
-\subsection{Algorithms}
-
-Algorithms should be formatted using standard algorithm packages where possible, as in Algorithm~\ref{alg:1}.
-
-\begin{algorithm}[htb]
-\caption{Example algorithm formatting after \cite{zhong16.IJGIS}} \label{alg:1}
-\footnotesize
-\begin{algorithmic} [1]                   % enter the algorithmic environment
-\Require A finite set of two-dimensional points $P \subset \mathbb{R} \times \mathbb{R}$ and one parameter $\lambda \in \mathbb{R}$
-\State Construct the Delaunay triangulation $DT(P)$ of $P$
-\State $\Delta \gets DT(P)$
-\State Construct the list $B$ of exterior edges of $DT(P)$
-\State Sort the list $B$ in descending order of edge length
-\State Initialize the $v\!-\!boundary$ function
-\State Set the root ($r$) of $\mathbf{T}_{{\chi}}(P,\, \lambda)$ to be \{edge = $\emptyset$, oppositeVertex = $\emptyset$, length = $\emptyset$\} 
-\State Construct the list of parent nodes ($PN$) for the elements in $B$
-\State Set each element in $PN$ to be $r$
-\State $O(P,\, \lambda) \gets \emptyset$
-\While{$B$ is not empty} 
-	\State $e = \{d_1,\, d_2\} \gets$ pop($B$)
-	\State $p \gets$ pop($PN$)
-	\State $o \gets$ opposite vertex of $e$ in $\Delta$
-	\State $N \gets$ \{edge = $e$, oppositeVertex = $o$, length = $||e||$\}
-	\State Insert $N$ in $\mathbf{T}_{{\chi}}(P,\, \lambda)$ as a child of $p$
-	\State $node(d_1) \gets N$
-	\State $node(d_2) \gets N$
-	\State Append $N$ to $O(P,\, \lambda)$
-	\If{$||e|| > \lambda$ \textbf{and} $v\!-\!boundary(o) = false$}
-		\State Remove $e$ from $\Delta$
-		\State $v\!-\!boundary(o) = true$
-		\State Insert the arms of $e$ in $\Delta$ into $B$ in order of edge length
-		\State Insert $N$ into $PN$ at the corresponding position of the arms of $e$ in $B$ 
-	\EndIf
-\EndWhile
-\State \textbf{Return} $\chi(P,\, \lambda)$ formed by leaves of $\mathbf{T}_{{\chi}}(P,\, \lambda)$, $DT(P)$, $\mathbf{T}_{{\chi}}(P,\, \lambda)$ and $O(P,\, \lambda)$
-\end{algorithmic}
-\end{algorithm}
-
-\subsection{Footnotes}
-Footnotes are strongly discouraged in text. Where footnotes must be used, they should be numbered consecutively.
-
-\section{References}
-References must be listed in the numerical system (ACM).
-Citations must be numbered sequentially [in square brackets] in the main text.
-Full numbered references must be listed in the reference section in alphabetical order.
-The reference numbers must be finalized and the bibliography must be fully formatted before submission.
-Examples of citation styles included in the bibliography for this document include journal articles \cite{overEtAl2010,arkin}, authored books \cite{bailey}, edited books \cite{miller09.BOOK}, articles in proceedings \cite{champion11}, articles in books or collections \cite{Grosso12}, theses \cite{ruas99}, technical reports \cite{blasertr}, and web resources \cite{web}.
-
-\subsection{DOIs}
-
-All JOSIS articles must list the DOI of all references, where a DOI exists, see
-\url{http://josis.org/index.php/josis/about/submissions#authorGuidelines} for examples. Please check carefully to add the DOIs for cited references,
-adding DOIs to all references that have one. DOIs may be added in the ``doi'' field of the bibtex file.
-
-DOIs can be found via \url{http://www.crossref.org/guestquery/} as well as many
-other search engines and publisher pages (e.g., Scopus, SpringerLink).
-
-\section{About JOSIS}
-
-The Journal of Spatial Information Science (JOSIS) is an international, interdisciplinary, open-access journal dedicated to publishing high-quality, original research articles in spatial information science.
-The journal aims to publish research spanning the theoretical foundations of spatial and geographical information science, through computation with geospatial information, to technologies for geographical information use.
-
-JOSIS encourages submissions from topics including, but not limited to spatial and spatiotemporal information systems; computational geometry, geocomputation, spatial algorithms; geovisualization, cartography, and geographical user interfaces; computing with spatiotemporal information under uncertainty; spatial cognition and qualitative spatial reasoning; spatial data models and structures; conceptual models of space and geoontology; distributed and parallel spatial computing, web-based GIS, and interoperability; context- and location-aware computing; and applications to GIS, spatial databases, location-based services, geosensor networks, and geosensor web.
-The journal publishes full-length original research articles, as well as survey-style review papers.
-In addition, the journal publishes shorter articles in three sections: reports from community activities, letters to the editors, and book reviews.
-
 \section*{Acknowledgments}

### 2024-12-17 article/main.tex
update josisexample.bib to remove obsolete entries and add new references for Go, Ionic, and MariaDB

@@
-%% josis.tex 1.4   2016-09-15    JoSIS latex template
+% josis.tex 1.4   2016-09-15    JoSIS latex template
 %------------------------------------------------------------------
@@
    number=N, year=YYYY, firstpage=xx, lastpage=yy, 
-  doi={10.5311/JOSIS.YYYY.II.NNN},
+  doi={10.5311/JOSIS.\textit{TBD}},
    received={December 18, 2024}, 
-   returned={},
+   returned={\textit{TBD}},
    revised={},
@@
 % Add 5-10 keywords for every submission
-\keywords{Web Application, Wildlife Sightings, Geodata, Open Source, Web Frameworks}
+\keywords{Web Application, Wildlife Sightings, Geodata, Field Recording, Web Frameworks}
 
@@
 available online with the option to install it on smartphones of all major operating systems.
-The project was a success and the technology is accessible to everyone with a bit more than basic programming knowledge and maybe some help.
+The project was a success and the technology is accessible to everyone with a bit more than basic programming knowledge, some help and some 
+insane persistence.
 
@@
 
-\section{Author guidelines}
+At the heart of any project involving geospatial data are the data themselves. If these data are not yet available, 
+the goal is to find an appropriate method to collect them. In the field of environmental sciences, 
+data collection still often relies on manual methods. However, this fieldwork can also be simplified through the use of technology. 
+A suitable tool for this purpose is something almost everyone possesses -- a smartphone.
+A quick online search reveals that there are already many apps available that can accomplish this. 
+However, these are often relatively expensive, offer far more features than actually needed, 
+and control over the data often lies with the app provider. With all the modern frameworks 
+and programming languages available today, it should not be that difficult to write a 
+custom app that does exactly what is required.
+And so, the idea to create a custom app was born.
+In this case an example to record wildlife sightings was chosen as the use case.
+The general idea is to create an individual toolkit from wich future use cases can be derived. 
+This work aims to examine just how challenging it really is to develop an app, 
+particularly with very limited prior knowledge, a lot of trial and error, 
+extensive research, the use of AI, immense patience, 
+and a bit to significantly more support from an experienced developer.
+
+It was with this support that the project began. To avoid having to figure everything out from scratch, 
+the process started with a consultation. During this meeting, the idea was presented, 
+and discussions were held on which technologies, programming languages, 
+and frameworks would be practical, feasible, and sensible. 
+In a subsequent session, the server was configured, and the development environment was set up together. 
+A not-so-small crash course then provided a solid foundation for diving into the project.
+
+\section{Methods}
+
+The app essentially consists of three parts: the web-based frontend, the backend server, 
+and the database. These three components are interconnected and communicate with each other. 
+The frontend is the user interface displayed on the smartphone, 
+the backend handles the logic running in the background, 
+and the database serves as the storage location for all data that is retrieved or saved.
+
+\subsection{Frontend}
+
+The frontend was created using the Ionic framework. Ionic is an open-source toolkit for 
+developing mobile user interfaces. It is based on Angular, another open-source framework developed by Google. 
+Ionic enables the creation of web applications that run on all platforms -- Android, iOS, and web -- while 
+offering native app-like performance and experience \cite{IonicFrameworkCrossPlatform}.
+The framework makes it relatively easy to start a project and test it in a development environment, 
+where the app is displayed in the browser. The actual programming is done using the programming 
+languages HTML, CSS, and TypeScript. TypeScript is a programming language developed by Microsoft that is based on JavaScript. 
+CSS is a stylesheet language used for designing the user interface, while HTML is a markup language used for structuring the user interface.
+
+\subsection{Backend}
+
+The backend was created using the programming language Go. Go is a programming language developed 
+by Google that is used for the development of web applications and servers. 
+It is easy to learn and use and offers good performance \cite{GoProgrammingLanguage}.
+It is also worth mentioning that GitHub Copilot provides excellent suggestions for 
+the Go programming language, which significantly simplifies programming. The main logic handled 
+by the backend in the app includes user authentication, accessing the database to check for available 
+users or retrieve options for animals, and transforming and saving new data in the database.
+
+\subsection{Database}
+
+The database used is MariaDB. MariaDB is a relational database derived from MySQL and developed by the open-source community. 
+It is easy to install and use and offers good performance \cite{MariaDBFoundation}.
+In this case, Docker was used to install the database on the server and run it in a so-called container. 
+The database consists of three tables: \texttt{users}, \texttt{tierarten}, and \texttt{sichtungen}, 
+where \texttt{tierart\_id} and \texttt{user\_id} are used as foreign keys in the \texttt{sichtungen} table. 
+The ER diagram of the database is shown in Figure~\ref{fig:db_structure}.
+
+\begin{figure}[tbh]
+    \centering
+    \includegraphics[width=0.6\textwidth]{images/db_structure.png}
+    \caption{ER Diagram of the database}\label{fig:db_structure}
+\end{figure}
+
+\subsection{WebMap}
+
+A final component used in the app is a WebMap. This is retrieved directly from the frontend 
+via Google Web Services and embedded into the app. To enable this, 
+a Google developer account is required to create a WebMap, 
+which can then be accessed using a MapID. Configurations regarding the appearance of the map can be made directly in the Google developer account.
+
+\subsection{Design}
+
+The design of the app is really quite simple. In general it just uses the default styling of the Ionic framework with very minor adjustments.
+The only patt where some effort was put in was the logo. The logo was designed by a fellow student and is shown in Figure~\ref{fig:logo}.
+The idea is to vertically show the general purpose of recording geo tagged data. Horizontally it symbolizes the data content of the app.
+So for future use cases the logo can be easily adjusted to fit the new content.
+\begin{figure}[tbh]
+    \centering
+    \includegraphics[width=0.4\textwidth]{images/logo_app.png}
+    \caption{Logo for the app}\label{fig:logo}
+\end{figure}
+
+\section{Results}
+
+\subsection{Web Application}
+
+The app was successfully developed and deployed. And will be available for a few months after the submission of this report.
+It seems a bit pointless to describe the app in detail here, as it is available online and can be tested by anyone.
+To install the app on a smartphone just use the qr code in Figure~\ref{fig:qr_code_app} or visit 
+the website \url{https://wildtierapp.juliankraft.ch/app/}. On opening the page a prompt will suggest the installation of the app.
+It works best using the Google Chrome browser. In order for the app to work, location services must be enabled on the smartphone
+and the app must be granted access to the location.
+
+\begin{figure}[tbh]
+    \centering
+    \includegraphics[width=0.3\textwidth]{images/qr_code_app.png}
+    \caption{QR Code to install the app}\label{fig:qr_code_app}
+\end{figure}
+
+\subsection{Data View}
+
+In addition to the app, a data view was created to display the data collected by the app. It is publicly available and can be 
+accessed at \url{https://wildtierapp.juliankraft.ch/}. This works best using the Google Chrome browser on a computer.
+
+\subsection{Data Access}
+
+This data view is only a frontend to display the data. In order to access the data for further processing, a REST API was created.
+A python script to access the data and a config file for a read only user is available on the GitHub repository 
+for the backend under \path{./db_setup/}.
+Feel free to use this script to and config file to access the data for testing. However the data is not valid since it was created for testing purposes only
+and anyone testing the app can add random data to the database.
+
+\subsection{Code Base}
+All the code for the app is publicly available on GitHub. 
+\begin{itemize}
+    \item Frontend: \url{https://github.com/juliankraft/WildtierSichtungsApp_front}
+    \item Backend: \url{https://github.com/juliankraft/WildtierSichtungsApp_back}
+\end{itemize}
+
+\section{Discussion}
 
@@
 
-Acknowledgments appear in a separate unnumbered section before the bibliography.
-Please acknowledge anyone (individual/company/institution) who has contributed to the study, including substantial contributions to the conception, design, acquisition of data; analysis and interpretation of data; drafting the manuscript; or provided critical comments resulting in revisions to content.
-For each author, please list the source(s) of any funding or financial contributions related to the study.
+I would like to express my gratitude to Ramon Ott -- the experienced developer -- for his help and support during this project. 
+Without his help, this project would not have been possible.
+I very much appreciate the help of my fellow student Annalisa Berger for her great work on the design of the logo for the application.
+
+\section*{Declarations}
+
+The creation of this document was supported by ChatGPT and GitHub Copilot. 
+Additionally, AI played a significant role in the development of the prototype.
+The Introduction and the Methods section where translated from German to English using
+ChatGPT since they where written before realizing that this report had to follow the JOSIS template
+specifically defining the language.
 

### 2024-12-17 article/main.tex
update main.tex to include links to frontend and backend repositories; clarify the open-source nature of the code

@@
 \subsection{Code Base}
-All the code for the app is publicly available on GitHub. 
+All the code for the app is publicly available on GitHub:
 \begin{itemize}
@@
 \end{itemize}
+
+It is worth mentioning that the code is not perfect -- at this point it is not more than a working prototype. Still the code is open source and can
+be used by anyone to do whatever under the creative commons license CC0 1.0 Universal.
 

### 2024-12-18 article/main.tex
update .gitignore to exclude 'bericht/' directory; normalize keywords in main.tex
Discussion section written

@@
 % Add 5-10 keywords for every submission
-\keywords{Web Application, Wildlife Sightings, Geodata, Field Recording, Web Frameworks}
+\keywords{web application, wildlife sightings, geodata, field recording, web frameworks}
 
@@
 
+It seems that the technology to create a web application to record geo tagged data is accessible to everyone with a bit more than basic programming knowledge,
+some help and some insane persistence. The app was successfully developed and deployed. The data view was created and the data can be accessed via a REST API.
+Still it was a real struggle to get to this point and the hours put into this project are countless. The technology is accessible but the learning curve is steep.
+It is hard to determine if the accessability is more a result of modern frameworks or the fast improving AI tools like GitHub Copilot and ChatGPT.
+
+The biggest challenge was to keep an overview of all the components and how they interact with each other. For every part of the app there are countless
+files and modules somehow connected to each other. Especially the frontend was a real struggle. After the simple command \texttt{ionic start} and
+taking a few initial decisions, the project folder initiated by the framework is already filled with a lot of files and folders rather cryptic to a beginner. While AI is
+very strong in writing functions or limited parts of the code it is not very helpful in keeping an overview of the whole project.
+That seems to be where the real challenge lies.
+
+\subsection{Next Steps}
+
+The App is at this point a working prototype. A first step would be to further clean up the code and make it more readable before adding more to it.
+There are a few things that would need some more work. A especially important one would be the spatial data and its accuracy.
+Questions to follow up on would be: Is there a way to maximize the accuracy of the phone location? 
+How to handle the accuracy of the manually imputed location?
+An other important thing to work on would be the app control elements. While the idea was to keep the app as simple as possible,
+a bit more control would be nice. For example the possibility to go back to the previous screen to change the input.
+A data view within the app could be a nice feature especially the option to delete data points
+in order for the user to correct mistakes.
+
+In order for this things to be implemented and the project being taken further, an actual use case would be needed.
+It can be a bit frustrating to work on a project, intense like this one, without a real use case.
+With an actual use case there would be a clear goal and therefore a clear path to follow. For example the
+data structure would not be as generic and some real considerations there could improve the app.
+An other very important thing provided by a real use case would be an actual user group testing the app.
+
 \section*{Acknowledgments}

### 2024-12-18 article/main.tex
some adjustments

@@
 \runningauthor{\begin{minipage}{.9\textwidth}\centering Julian Kraft\end{minipage}}
-\runningtitle{Wildlife sightings WebApp}
+\runningtitle{Wildlife sightings -- a WebApp}
 
@@
 % Add 5-10 keywords for every submission
-\keywords{web application, wildlife sightings, geodata, field recording, web frameworks}
+\keywords{
+    web application development, 
+    wildlife monitoring, 
+    geospatial data, 
+    user authentication, 
+    frontend frameworks, 
+    backend programming, 
+    database management, 
+    rest api integration, 
+    mobile web apps, 
+    ionic and angular frameworks
+    }
 
@@
 \begin{abstract}
-The aim of this semester project is to assess the accessability of the technology to create a web application to record geo tagged data.
-With the help of modern web frameworks, a web application was built to record wildlife sightings. A working prototype was created and and made
-available online with the option to install it on smartphones of all major operating systems.
-The project was a success and the technology is accessible to everyone with a bit more than basic programming knowledge, some help and some 
-insane persistence.
+
+The project aimed to evaluate the accessibility of modern technology for creating a web application 
+that records geotagged data. Using modern web frameworks, a prototype was developed to document wildlife sightings. 
+This application, accessible online and installable on smartphones across major operating systems, 
+exemplifies how a straightforward and purpose-driven tool can be built with moderate programming knowledge, 
+guided support, and persistence. The project's workflow encompassed backend development in Go, 
+frontend design with the Ionic framework, and database integration using MariaDB. Additionally, 
+the system incorporates a public data visualization tool and REST API for broader access. 
+While the project highlights the potential of current technologies and AI-powered tools like GitHub Copilot, 
+it underscores challenges in managing interconnected components. The result is a versatile platform, 
+demonstrating both the promise and complexity of custom web application development for geospatial data collection.
 
@@
 and the database serves as the storage location for all data that is retrieved or saved.
+There is a separated frontend component, a static page,
+for the data view which is publicly available and can be accessed via a web browser.
 
@@
 languages HTML, CSS, and TypeScript. TypeScript is a programming language developed by Microsoft that is based on JavaScript. 
-CSS is a stylesheet language used for designing the user interface, while HTML is a markup language used for structuring the user interface.
+CSS is a stylesheets language used for designing the user interface, while HTML is a markup language used for structuring the user interface.
+
+There are two main pages implemented in the frontend. The home page dealing with user authentication and 
+the animals page where the user can input data. The home page is the first page displayed when the app is opened.
+There ist two options: to create a user or to log in. Upon successful authentication the user is directed to the
+animals page. Here there is a stepper at work in the background. Upon completion of a step, the stepper is increased
+by one triggering a different view for the next step. This is all handled by the frontend itself. Only fetching and saving
+data are handled by the backend.
 
@@
 users or retrieve options for animals, and transforming and saving new data in the database.
+
+It is structured into a few files. There is the main file \texttt{main.go} where the server is started and the routes are defined.
+And there are three different handlers files to handle processes concerning login, animal sightings and the requests of the static
+page for the data view.
 
@@
 
+The app was successfully developed and deployed. It will be available for a few months after the submission of this report.
+It seems a bit pointless to describe the app in detail here, as it is available online and can be tested by anyone.
+This part of the report will therefore be kept short. The actual use of the app is supposed to be experienced by the user.
+
 \subsection{Web Application}
 
-The app was successfully developed and deployed. And will be available for a few months after the submission of this report.
-It seems a bit pointless to describe the app in detail here, as it is available online and can be tested by anyone.
 To install the app on a smartphone just use the qr code in Figure~\ref{fig:qr_code_app} or visit 
@@
 
-\section*{Declarations}
+\section*{AI Declarations}
 
@@
 The Introduction and the Methods section where translated from German to English using
-ChatGPT since they where written before realizing that this report had to follow the JOSIS template
-specifically defining the language.
+ChatGPT since they where written before realizing, this report had to follow the JOSIS template,
+specifically defining the language. The abstract was initially generated by ChatGPT
+and than edited by the author.
 

### 2024-12-18 article/main.tex
spell check by ChatGPT

@@
 
-% Document begins
 \begin{document}
@@
 
-% Insert your own title
-\title{A Web Application for Wildlife Sightings - how accessible is this technology using modern frameworks?}
+\title{A Web Application for Wildlife Sightings - How Accessible Is This Technology Using Modern Frameworks?}
 
-% Insert your manuscipts authors, affiliations, and addresses
+% Insert your manuscript authors, affiliations, and addresses
 \author{Julian Kraft}\affil{LSFM, ZHAW, Switzerland}
@@
 And so, the idea to create a custom app was born.
-In this case an example to record wildlife sightings was chosen as the use case.
-The general idea is to create an individual toolkit from wich future use cases can be derived. 
+In this case, an example to record wildlife sightings was chosen as the use case.
+The general idea is to create an individual toolkit from which future use cases can be derived. 
 This work aims to examine just how challenging it really is to develop an app, 
@@
 extensive research, the use of AI, immense patience, 
-and a bit to significantly more support from an experienced developer.
+and significantly more support from an experienced developer.
 
@@
 and the database serves as the storage location for all data that is retrieved or saved.
-There is a separated frontend component, a static page,
+There is a separate frontend component, a static page,
 for the data view which is publicly available and can be accessed via a web browser.
@@
 
-There are two main pages implemented in the frontend. The home page dealing with user authentication and 
+There are two main pages implemented in the frontend. The home page deals with user authentication and 
 the animals page where the user can input data. The home page is the first page displayed when the app is opened.
-There ist two options: to create a user or to log in. Upon successful authentication the user is directed to the
+There are two options: to create a user or to log in. Upon successful authentication, the user is directed to the
 animals page. Here there is a stepper at work in the background. Upon completion of a step, the stepper is increased
-by one triggering a different view for the next step. This is all handled by the frontend itself. Only fetching and saving
+by one, triggering a different view for the next step. This is all handled by the frontend itself. Only fetching and saving
 data are handled by the backend.
@@
 It is structured into a few files. There is the main file \texttt{main.go} where the server is started and the routes are defined.
-And there are three different handlers files to handle processes concerning login, animal sightings and the requests of the static
+And there are three different handler files to handle processes concerning login, animal sightings, and the requests of the static
 page for the data view.
@@
 
-The design of the app is really quite simple. In general it just uses the default styling of the Ionic framework with very minor adjustments.
-The only patt where some effort was put in was the logo. The logo was designed by a fellow student and is shown in Figure~\ref{fig:logo}.
-The idea is to vertically show the general purpose of recording geo tagged data. Horizontally it symbolizes the data content of the app.
-So for future use cases the logo can be easily adjusted to fit the new content.
+The design of the app is really quite simple. In general, it just uses the default styling of the Ionic framework with very minor adjustments.
+The only part where some effort was put in was the logo. The logo was designed by a fellow student and is shown in Figure~\ref{fig:logo}.
+The idea is to vertically show the general purpose of recording geo-tagged data. Horizontally it symbolizes the data content of the app.
+So for future use cases, the logo can be easily adjusted to fit the new content.
 \begin{figure}[tbh]
@@
 
-To install the app on a smartphone just use the qr code in Figure~\ref{fig:qr_code_app} or visit 
+To install the app on a smartphone just use the QR code in Figure~\ref{fig:qr_code_app} or visit 
 the website \url{https://wildtierapp.juliankraft.ch/app/}. On opening the page a prompt will suggest the installation of the app.
@@
 This data view is only a frontend to display the data. In order to access the data for further processing, a REST API was created.
-A python script to access the data and a config file for a read only user is available on the GitHub repository 
+A Python script to access the data and a config file for a read-only user is available on the GitHub repository 
 for the backend under \path{./db_setup/}.
-Feel free to use this script to and config file to access the data for testing. However the data is not valid since it was created for testing purposes only
+Feel free to use this script and config file to access the data for testing. However, the data is not valid since it was created for testing purposes only
 and anyone testing the app can add random data to the database.
@@
 
-It is worth mentioning that the code is not perfect -- at this point it is not more than a working prototype. Still the code is open source and can
+It is worth mentioning that the code is not perfect -- at this point, it is not more than a working prototype. Still, the code is open source and can
 be used by anyone to do whatever under the creative commons license CC0 1.0 Universal.
@@
 
-It seems that the technology to create a web application to record geo tagged data is accessible to everyone with a bit more than basic programming knowledge,
-some help and some insane persistence. The app was successfully developed and deployed. The data view was created and the data can be accessed via a REST API.
-Still it was a real struggle to get to this point and the hours put into this project are countless. The technology is accessible but the learning curve is steep.
-It is hard to determine if the accessability is more a result of modern frameworks or the fast improving AI tools like GitHub Copilot and ChatGPT.
+It seems that the technology to create a web application to record geo-tagged data is accessible to everyone with a bit more than basic programming knowledge,
+some help, and some insane persistence. The app was successfully developed and deployed. The data view was created and the data can be accessed via a REST API.
+Still, it was a real struggle to get to this point, and the hours put into this project are countless. The technology is accessible, but the learning curve is steep.
+It is hard to determine if the accessibility is more a result of modern frameworks or the fast-improving AI tools like GitHub Copilot and ChatGPT.
 
-The biggest challenge was to keep an overview of all the components and how they interact with each other. For every part of the app there are countless
+The biggest challenge was to keep an overview of all the components and how they interact with each other. For every part of the app, there are countless
 files and modules somehow connected to each other. Especially the frontend was a real struggle. After the simple command \texttt{ionic start} and
 taking a few initial decisions, the project folder initiated by the framework is already filled with a lot of files and folders rather cryptic to a beginner. While AI is
-very strong in writing functions or limited parts of the code it is not very helpful in keeping an overview of the whole project.
+very strong in writing functions or limited parts of the code, it is not very helpful in keeping an overview of the whole project.
 That seems to be where the real challenge lies.
@@
 
-The App is at this point a working prototype. A first step would be to further clean up the code and make it more readable before adding more to it.
-There are a few things that would need some more work. A especially important one would be the spatial data and its accuracy.
+The App is, at this point, a working prototype. A first step would be to further clean up the code and make it more readable before adding more to it.
+There are a few things that would need some more work. An especially important one would be the spatial data and its accuracy.
 Questions to follow up on would be: Is there a way to maximize the accuracy of the phone location? 
-How to handle the accuracy of the manually imputed location?
-An other important thing to work on would be the app control elements. While the idea was to keep the app as simple as possible,
-a bit more control would be nice. For example the possibility to go back to the previous screen to change the input.
+How to handle the accuracy of the manually input location?
+Another important thing to work on would be the app control elements. While the idea was to keep the app as simple as possible,
+a bit more control would be nice. For example, the possibility to go back to the previous screen to change the input.
 A data view within the app could be a nice feature especially the option to delete data points
@@
 
-In order for this things to be implemented and the project being taken further, an actual use case would be needed.
+In order for these things to be implemented and the project being taken further, an actual use case would be needed.
 It can be a bit frustrating to work on a project, intense like this one, without a real use case.
-With an actual use case there would be a clear goal and therefore a clear path to follow. For example the
+With an actual use case, there would be a clear goal and therefore a clear path to follow. For example, the
 data structure would not be as generic and some real considerations there could improve the app.
-An other very important thing provided by a real use case would be an actual user group testing the app.
+Another very important thing provided by a real use case would be an actual user group testing the app.
 
@@
 Additionally, AI played a significant role in the development of the prototype.
-The Introduction and the Methods section where translated from German to English using
-ChatGPT since they where written before realizing, this report had to follow the JOSIS template,
+The Introduction and the Methods section were translated from German to English using
+ChatGPT since they were written before realizing, this report had to follow the JOSIS template,
 specifically defining the language. The abstract was initially generated by ChatGPT
-and than edited by the author.
+and then edited by the author.
 

### 2024-12-18 report/main.tex
Add josisexample.bib for references and update README with project details

--- 2024-12-18 article/main.tex
@@
     database management, 
-    rest api integration, 
     mobile web apps, 
@@
 frontend design with the Ionic framework, and database integration using MariaDB. Additionally, 
-the system incorporates a public data visualization tool and REST API for broader access. 
+the system incorporates a public data visualization tool and direct database access. 
 While the project highlights the potential of current technologies and AI-powered tools like GitHub Copilot, 
@@
 
-This data view is only a frontend to display the data. In order to access the data for further processing, a REST API was created.
+This data view is only a frontend to display the data. In order to access the data for further processing, a direct database access is available.
 A Python script to access the data and a config file for a read-only user is available on the GitHub repository 
@@
 It seems that the technology to create a web application to record geo-tagged data is accessible to everyone with a bit more than basic programming knowledge,
-some help, and some insane persistence. The app was successfully developed and deployed. The data view was created and the data can be accessed via a REST API.
+some help, and some insane persistence. The app was successfully developed and deployed. The data view was created and the data can be accessed via a direct database access.
 Still, it was a real struggle to get to this point, and the hours put into this project are countless. The technology is accessible, but the learning curve is steep.
@@
 Without his help, this project would not have been possible.
+
 I very much appreciate the help of my fellow student Annalisa Berger for her great work on the design of the logo for the application.
@@
 
-The creation of this document was supported by ChatGPT and GitHub Copilot. 
-Additionally, AI played a significant role in the development of the prototype.
-The Introduction and the Methods section were translated from German to English using
-ChatGPT since they were written before realizing, this report had to follow the JOSIS template,
-specifically defining the language. The abstract was initially generated by ChatGPT
-and then edited by the author.
+\begin{itemize}
+    \item The creation of this document was supported by ChatGPT and GitHub Copilot.
+    \item AI played a significant role in the development of the prototype.
+    \item The Introduction and the Methods sections were translated from German to English using ChatGPT 
+        since they were written before realizing this report had to follow the JOSIS template, specifically defining the language.
+    \item The Abstract was initially generated by ChatGPT and then edited by the author.
+    \item A complete spellcheck was performed using ChatGPT.
+\end{itemize}
 
